### 2018-09-07 manuscript.tex
Update manuscript.tex

\subsection{Research Questions}\label{research-questions}
The main focus of this study is to analyze attitudes of FGC benefits (see the list of FGC benefits at table xx) and of FGC continuance in association with intention (planned behavior) to cut daughters.  Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits and intention (planned behavior) of cutting daughters (structural models) in the hope of???

@@

The main constrcuts analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} (to confirm and update). The heory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  In this study, the attitudes referred to xx questions of FGC benefits in DHS (see the list of FGC benefits at table-- in Appendix); perceived behavioral control as to perception of domestic violence and social resources (wealth, education, media use and job?); and the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory.

@@

The main response variables were woman's attitude on whether they think FGC should be continued in the FGC future model and woman's intention of cutting their daughters in the daughter's FGC status model.  The main predictors in both of the models were attitudes of FGC benefits and woman's FGC status.  We also included woman's gender awareness (see the list of attitudes towards violence against women at table xx) as proxy to gender theory, and wealth and media use (For details, see table xx in appendix) to modernization theory.  It is noted that we chose woman's attitudes towards gender violence instead of personal violence experience from their spouse because the former better reflects gender awareness.  We believed that FGC benefits coded and the information of such collected by DHS represented the values of the communities where FGC practiced.

In reference to the studies mentioned above, we also included the followings as covariates:  age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, and residence (urban vs. rural).  The followings were treated as random variables:  cluster ID (villages), countries and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).  Further, media effect was also counted in the random effect (slope?) because we presumed that each country carried various media content from each other.

 \_\_{[}CF:Do we spline wealth and group age? How do we estimate FGC belief, attitudes towards violence against women and media use?{]}

@@

In order to address the significance of community impact on the practice of FGC, we tested education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level, which represented the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, OdukAfol17}).  Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?)

\_\_{[}CF: Did we calculate FGC prevalence by counting all the women in the DHS, or just those with daughters in the daughter model?{]}
\_\_{[}CF:cluster is not a random effect in FGC, is it?{]}
\_\_{[}CF:Shall we also test religion and ethnicity at a community level?{]}
\_\_{[}JD: Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess. CF: Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  Same reason as for clusterID{]}

\_\_{[}CF:reason why using PCA:  see \cite{Hayf05} p.. 129 for reference.{]}
\_\_{[}CF:The concept of heterogeneity and threshold is important.  How to address these 2 concepts, if necessary.{]}
\_\_{[}CF:Spatial Bayesian model \cite{KandNwak09} "Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level. Consequently, the spatial analysis will be affected by some random fluctuations.  Some of this random variation can be reduced through structured spatial effects because it includes neighboring observations in the analysis. However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p. 788){]}

% "attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}

@@

>>>>

\subsection{Research Questions}\label{research-questions}
The main focus of this study is to analyze associations of attitudes of FGC benefits (see the list of FGC benefits at table xx) and intention (planned behavior) to cut daughters.  Additionaly, we also study the association of attitudes of FGC benefits and of FGC continuance; and the association of attitudes of FGC benefits, FGC continuance and intention (planned behavior) of cutting daughters (structural models) (to explain why)

@@

The main constrcuts analyzing FGC practice were based on the theory of planned behavior \cite{Ajze91, Ajze02, ThomMadd92} (need more work). The theory of planned behaviors proposed that intentions to perform behaviors could be predicted from three determinants:  attitudes toward the behavior, subjective norms, and perceived behavioral control \cite{Ajze91}.  Attitudes refer to the degree of favorable or unfavorable evaluation to which a person has of the behavior; subjective norm refers to the perceived social pressure to or not to perform the behavior; and perceived behavioral control refers to perception of the ease or difficulty of performing such behaviors \cite{Ajze91}.  In this study, the attitudes referred to xx questions of FGC benefits in DHS (see the list of FGC benefits at table-- in Appendix); perceived behavioral control as to perception of domestic violence and social resources (wealth, education, and job?); and the perceived social pressures (subjective norms) were measured according to the community level of attitudes of FGC benefits and FGC prevalence to reflect the convention norms of FGC under the convention theory. \cf{need comments!!!}

@@

The main response variables were woman's intention of cutting their daughters in the daughter's FGC status model and the daughter-future model, and woman's attitude on whether they think FGC should be continued in the FGC future model .  The main predictors were attitudes of FGC benefits and woman's FGC status.  We also included woman's gender awareness (see the list of attitudes towards violence against women at table xx) as proxy to gender theory, and wealth and media use (For details, see table xx in appendix) to modernization theory.  It is noted that we chose woman's attitudes towards gender violence instead of personal violence experience from their spouse because the former better reflects gender awareness.  We believed that FGC benefits coded and the information of such collected by DHS represented the values of the communities where FGC practiced.

The sociodemographic variables included age, education, religion (see the list of religion recode at table xx in appendix; with a footnote on how we recoded it), marital status, work status, and residence (urban vs. rural).  The followings were treated as random variables:  cluster ID (villages), countries and ethnicity (see the list of ethnicity recode at table xx in appendix; with a footnote on how we recoded it).  Further, media effect was also counted in the random effect (slope?) because we presumed that each country carried various media content from each other.

In order to address the significance of community impact on the practice, FGC prevalence was calculated on a cluster level \CF{right?} and applied in the models as part of the (wording...). Cluster, which is usually larger than a village but small enough to be a social community, was used to represent a community level of impact \cite{Hayf05} (is Hayf05 correct or DHS method changes afterwards?).  We also tested education, wealth, media use, FGC beliefs, gender awareness and FGC prevalence at the community level, which represented the degrees of modernization, conventional values and gender awareness within- and among-community (see \cite{Achi14, BoylMcMo02, Hayf05, KandNwak09, ModrLiu13, OdukAfol17}).

 \_\_{[}CF:Do we splne wealth and group age? How do we estimate FGC belief, attitudes towards violence against women and media use?{]}

@@

\_\_{[}CF:cluster is not a random effect in FGC, is it?{]}
\_\_{[}JD: Ideally, we would make ethnicity a random effect, but we are back to the Gilmour problem I guess. CF: Ethnicity is an important factor (see Hayf05), more so than religion, associating with FGC status, and I don't think it shall be coded as a random factor.  Same reason as for clusterID{]}

\_\_{[}CF:The concept of heterogeneity and threshold is important.  How to address these 2 concepts, if necessary.{]}
\_\_{[}CF:Spatial Bayesian model \cite{KandNwak09} "Conversely, one cannot assume that the clusters selected in each district are fully representative of the states in which they are located because surveys only attempted to generate a fully representative sample at the regional level. Consequently, the spatial analysis will be affected by some random fluctuations.  Some of this random variation can be reduced through structured spatial effects because it includes neighboring observations in the analysis. However, it should be pointed out that such a spatial analysis should preferably be applied to census data, where the precision of the spatial analysis would be much higher." (p. 788){]}

-----stop reading -----
% "attitude is the strongest predictor of mothers' intentions to allow their daughters to undergo FGM, followed by subjective norms." \cite{PashPonn16}

@@

To study types of FGC for the future to understand correlation/assocaition between types of fgc and fgc beneifts.
